The Natural History of Child Signals of Need in Utila, Honduras: An Exploratory Study

### 2024-12-07 Paper.qmd
Minor edit in Results

In general, older child age and better neighborhoods were associated with less conflict and less signaling, whereas medical problems were associated with more conflict and more signaling. Alloparenting frequency was positively associated with signaling for girls, and negatively for boys.

>>>>

In general, older child age and better neighborhoods were associated with less conflict and less signaling, whereas medical problems were associated with more conflict and more signaling. There was little evidence for a sex difference in signaling, except that alloparenting frequency was positively associated with signaling for girls, and negatively for boys. Male sex was associated with more conflict.
